The Impact of Educational Expenses of New Coders

### 2021-04-26 outputs/paper/paper.Rmd
Edit text in paper.Rmd

## Casuality

>>>>

## Casuality
In addition to the low R-squared scores, there is another reason that causality cannot be explained from the regression models. In reality, there will be plenty of factors that actually affect beginner programmers’ expenses to learn to code besides those selected seven variables. For example, there might be some institutions where the programmers can learn to code near their home, or some of them might be heavily exposed to online advertisements of some online-learning platforms that teach programming. In other words, realistically, it is almost impossible to measure all the variables happening in the large world and include them in the model. However, we can always measure which variables are significant and determine the most appropriate variables to make a model closer to the reality. For future studies, I suggest running the same analysis process, from the correlation analysis to linear regression models and model validation, with other variables that are not covered in this paper. Also, surveys of other years can be used to compare the results of this analysis.
